---
title: "Final_Project_BigData_2019"
author: "Agus Setiyawan"
date: "4/18/2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

#Read Data
The data was collected on board for 5 months in 2015, it was collected by observer on the pole-and-line vessel. The fishing ground is only 2 different area in Indonesia, it called North of Sulawesi and South of Sulawesi. 
The CPUE is total catch/number of fishing at sea. 
The primary data inlcuding : Total catch, Fishing time, Fishing duration, Total trip, Fishing ground, Live-bait, etc. 

```{r setup, read the data}
skj <- read.csv("Data_new_EcoStat.csv", header = TRUE, sep = ",")
```

##Attach and names of the data set
```{r attach and names of the data set }
head(skj)
attach(skj)
names(skj)
```

##Plots
This is plot for total catch data:
```{r plots, Raw data plots}
plot(Total_Catch)
```

This is plot for log:
```{r plots log, Raw data plots log}
plot(log(Total_Catch))
```

This is plot for CPUE:
```{r plots CPUE, Raw data plots CPUE}
plot(CPUE)
```

This is boxplot for CPUE based on the Month:
```{r boxplots}
boxplot(CPUE~Month, xlab="Month", ylab="CPUE")
```

This is histogram plot for CPUE:
```{r histogram log CPUE}
hist(log(CPUE))
```

This is plotting for latitude and longitude:
```{r plot for long and lat}
plot(Long,Lat)
```

#Create the Model
this is how to create the model based on the data.

##Model 1
#this model is calculated the linear model based on the fishing ground, time to fishing according to 5 Month
```{r model 1}
mod1 = lm(CPUE~as.factor(Time) + as.factor(Fishing_Ground) + as.factor(Month))
mod1
anov1 <- aov(mod1)
summary (anov1)
```

##Model 2
#this model is calculated the linear model based on the type of live bait has used on the fishing ground according to 5 Month
```{r model 2}
mod2 = lm(CPUE~as.factor(Live_Bait)+as.factor(Fishing_Ground) + as.factor(Month))
summary (mod2)
anov2 <- aov(mod2)
summary(anov2)
```

##Model 3
#this model is estimate the linear model based on the type live bait has used based on the Month and position

```{r model 3}
mod3 = lm(CPUE~as.factor(Live_Bait) + as.factor(Month) + Long + Lat)
summary(mod3)
anov3 <- aov(mod3)
summary(anov3)
```

##Model 4
#this model is to estimate the linear model by CPUE based on the fishing duration
```{r model 4}
mod4 = lm(CPUE~Fishing_Duration + as.factor(Live_Bait) + as.factor(Month))
summary (mod4)
anov4 <- aov(mod4)
summary(anov4)
```

## Model 5
#this model is to estsimate the linear model by CPUE based on the time of fishing
```{r model 5}
mod5 = lm(CPUE~as.factor(Time) + Fishing_Duration + Bait_Amount + as.factor(Month))
summary (mod5)
anov5 <- aov(mod5)
summary(anov5)
```

#Model 6 
#this model is to estimate the generalized linear model by CPUE
```{r model 6}
mod6 = glm(CPUE~poly(SST) + as.factor(Month) + as.factor(Time) + Long + Lat +
             Fishing_Duration + Bait_Amount, family = gaussian)
summary(mod6)
plot(mod6)
anov6 <- aov(mod6)
summary(anov6)
```

##Model 7
#this model is to estimate which live Bait influence to the total catch
```{r model 7}
mod7 = lm(Total_Catch~as.factor(Live_Bait), family = gaussian)
summary (mod7)
plot(mod7)
anov7 <- aov(mod7)
summary(anov7)
```

#If the result showed that the time of the fishing is significant affect to the CPUE, 
#we can assumed that fish behavior od skipjack tuna has a feeding behaviour on that time
#based on the result we can try to use t test, to estimate how it works

#model 8
```{r model 8}
mod8 = glm(Total_Catch~as.factor(Time), family = gaussian)
summary(mod8)
plot(mod8)
anov8 <- aov(mod8)
summary(anov8)
```

#model 9
#this model inform  that the value of the R-suared 0.1497, it means that the time as factor 
#is significcant because the P value 0.002916 (not close to 0)
```{r model 9}
mod9 = lm(Total_Catch~as.factor(Time), family = gaussian)
summary (mod9)
anov9 <- aov(mod9)
summary(anov9)
```

#model 10
#this medel inform that the value of the R-squared 0.08, it means that significant linear
#to the total catch, but the p value 0.1089
```{r model 10}
mod10 = lm(Total_Catch ~as.factor(Live_Bait), family = gaussian)
summary (mod10)
```

#Create the function of a
#Function a
```{r install ggplot}
library(ggplot2)
```

```{r function a}
a <- ggplot(skj, aes( x = Total_Catch, y = Bait_Amount, color = CPUE))
a + geom_point()
a + geom_point() + facet_wrap(~Month)
a + geom_point() + facet_wrap(~Time)
a + geom_point() + facet_wrap(~Live_Bait)
a + geom_point() + facet_wrap(~Fishing_Ground)
```

#Create the function of b
#Function b
```{r function b}
b <- ggplot(skj, aes( x = Total_Catch, y = Fishing_Duration, color = CPUE))
b + geom_point()
b + geom_point() + facet_wrap(~Month)
b + geom_point() + facet_wrap(~Time)
b + geom_point() + facet_wrap(~Live_Bait)
b + geom_point() + facet_wrap(~Fishing_Ground)
```

#Create the function of c
#Function c 
```{r function c}
c <- ggplot(skj, aes( x = Total_Catch, y = CPUE, color = SST))
c + geom_point()
c + geom_point() + facet_wrap(~Month)
c + geom_point() + facet_wrap(~Time)
c + geom_point() + facet_wrap(~Live_Bait)
c + geom_point() + facet_wrap(~Fishing_Ground)
```

#Plot the relationship between Fishing Duration and Bait Amount to CPUE based on the Month
```{r ggplot CPUE vs Month}
ggplot(skj,aes( x = Total_Catch, y = Fishing_Duration)) + geom_point() + geom_smooth(method="lm") + facet_wrap(~Time)
ggplot(skj,aes( x = Total_Catch, y = Fishing_Duration)) + geom_point() + geom_smooth(method="lm") + facet_wrap(~Live_Bait)
ggplot(skj,aes( x = Total_Catch, y = Bait_Amount)) + geom_point() + geom_smooth(method="lm") + facet_wrap(~Live_Bait)
ggplot(skj,aes( x = Total_Catch, y = Fishing_Duration)) + geom_point() + geom_smooth(method="lm") + facet_wrap(~Time)
ggplot(skj,aes( x = Total_Catch, y = Bait_Amount)) + geom_point() + geom_smooth(method="lm") + facet_wrap(~Time)
```

## The Linear Regression Plotting
#Plot the linear model by the Bait Amount and Total Catch
```{r plot regress 1}
plot (Bait_Amount,Total_Catch, file = skj)
z <- line(Bait_Amount, Total_Catch)
abline(coef(z))
cor(Bait_Amount,Total_Catch)
```

#Plot the linear model by the Fishing Duration and Total Catch
```{r plot regress 2}
plot (Fishing_Duration, Total_Catch, file = skj)
z <- line (Fishing_Duration, Total_Catch)
abline(coef(z))
cor(Fishing_Duration,Total_Catch)
```

#Plot the linear model by the Bait Amount and CPUE
```{r plot regress 3}
plot (Bait_Amount, CPUE, file = skj)
z <- line(Bait_Amount,CPUE)
abline(coef(z))
cor(Bait_Amount, CPUE)
```

#Plot the linear model by the Fishing Duration and CPUE
```{r plot regress 4}
plot (Fishing_Duration,CPUE, file = skj)
z <- line(Fishing_Duration,CPUE)
abline(coef(z))
cor(Fishing_Duration, CPUE)
```

#Based on the GLM that the factor influence to the CPUE are fishing duration, time of fishing
#total live-bait and month
#the best live-bait to use is mixed between red anchovy and round scad
#the best time to fishing is around 12pm - 4pm
#the next possibilty research: what is the best size of hook to use (selectivity) based on the lenght of fish has caught and
#any differences between fishing on the FAD (fish agregating devices) and fish schooling


